Summary Tables

### 2020-03-02 summary_tables.Rmd
Keep help functions at top
Add trip prop and trip distance for all case studies, for baseline

@@

@@

@@

@@

for(city in cities){
  count_people <- nrow(io[[city]]$synth_pop)
  td <- io[[city]]$dist %>% filter(stage_mode != 'bus_driver') %>% mutate_if(is.numeric, round, digits = round_to) %>% mutate_if(is.numeric, list(~round((.) / count_people, round_to)))
  colnames(td)[3:7] <- rownames(scen_prop)

@@

@@

>>>>

```{r helper_functions, echo = F, message = F}

@@

trip_prop <- list()

@@

  td1 <- td %>% rownames_to_column()

  names(td1)[1] <- 'stage_mode'

  if (length(trip_prop) == 0){
    trip_prop <- td1 %>% dplyr::select(stage_mode)
  }

  td1 <- td1 %>% dplyr::select(stage_mode, baseline)

  trip_prop <- inner_join(trip_prop, td1, by = 'stage_mode')

@@

### Trip proportion Baseline
```{r}

kable(trip_prop)

@@

trip_dist <- list()

  count_people <- nrow(io[[city]]$synth_pop)
  td <- io[[city]]$dist %>% filter(stage_mode != 'bus_driver') %>% mutate_if(is.numeric, round, digits = round_to) %>% mutate_if(is.numeric, list(~round((.) / count_people, round_to)))
  colnames(td)[3:7] <- rownames(scen_prop)

@@

  td1 <- td

  if (length(trip_dist) == 0){
    trip_dist <- td1 %>% dplyr::select(stage_mode)
  }

  td1 <- td1 %>% dplyr::select(stage_mode, Baseline)

  trip_dist <- inner_join(trip_dist, td1, by = 'stage_mode')

@@

### Average distance Baseline
```{r}

kable(trip_dist)
